\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

 \usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
%\titleformat{\section}{
%  \vspace{-4pt}\scshape\raggedright\large
%}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%\titleformat{\section}{
	%	\vspace{-4pt}\scshape\bfseries\raggedright\large
	%}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\titleformat{\section}{
	\vspace{-4pt}\bfseries\MakeUppercase\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemAlt}[2]{
	\vspace{-2pt}
	\item\small{
		\textbf{#1}{#2 \vspace{-2pt}}
	}
}


\newcommand{\resumeSubheading}[4]{
  \vspace {-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2\\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingAlt}[6]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2\\
		\textit{\small#3} & \textit{\small #4} \\
		\textit{\small#5} & \textit{\small #6} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProject}[2]{
	\vspace {-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1}\\
		{\small\href{#2}{#2}} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize} }
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\usepackage{setspace}

\renewcommand{\baselinestretch}{1.5}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

	\justify

	\setstretch{1.5}
	%\onehalfspacing
%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\LARGE Yuri Pereira Marca} & Florianopolis, Brazil
	\\
	& Phone: +55 48 99976-2173 \\
	& Email: \href{mailto:yurimarca@gmail.com}{yurimarca@gmail.com} \\
	%& Website: \href{https://yurimarca.github.io}{https://yurimarca.github.io} \\
	& LinkedIn: \href{https://www.linkedin.com/in/yurimarca/}{https://www.linkedin.com/in/yurimarca/}

\end{tabular*}

%-----------Presentation Letter-----------------
\section{Presentation Letter}


I am an AI/ML Engineer and researcher with deep expertise in agentic AI systems, optimization, and MLOps, focused on compressing the cycle from research prototype to production deployment. I have architected production-grade multi-agent workflows (Google ADK, LangGraph), built retrieval-augmented generation systems grounding enterprise knowledge retrieval in live document corpora, and deployed full-stack AI services with automated LLM-as-Judge evaluation harnesses and end-to-end observability pipelines. My academic research spans Bayesian optimization, Monte Carlo Tree Search, and multi-objective evolutionary algorithms, having produced internationally recognized results including a Best Student Paper Award at EMO-2019 and multiple peer-reviewed publications that establish a rigorous, experiment-driven research foundation.

My industry experience covers the complete research-to-production cycle, from designing scalable, reproducible MLOps pipelines (MLflow, Docker, Kubernetes, AWS) for predictive maintenance and anomaly detection at WEG, to deploying low-latency voice AI and knowledge-grounded generation systems at Zazmic. I hold a Master's in Engineering from Shinshu University (MEXT Government Scholar) and a Bachelor's in Electronic Engineering, with international academic experience across Japan, the United Kingdom, and Canada.

I am motivated to contribute to research programs where agentic AI amplifies the depth and breadth of what a research team can accomplish, by designing parallel agent workflows, building automated experiment infrastructure, and shipping production-ready intelligent systems at scale.


%-----------PROFESSIONAL-EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Zazmic Inc}{United States of America (Remote)}
{AI/ML Engineer}{Dec. 2025 -- Present}
\resumeItemListStart
\resumeItem{Agentic AI Systems}{Architected production-grade multi-agent workflows using Google ADK and LangGraph, including ReAct agents for NL2SQL, Human-in-the-Loop (HITL) state management, and autonomous generators capable of ingesting diverse, multimodal unstructured data..}
\resumeItem{Real-Time Voice AI}{Engineered a low-latency, bidirectional voice agent utilizing WebSockets, FastAPI, and the Gemini Live API; implemented asynchronous tool definitions to support seamless, hands-free user interactions and real-time agent capabilities.}
\resumeItem{Retrieval-Augmented Generation}{Architected production RAG systems on GCP Vertex AI, grounding enterprise knowledge retrieval in live document corpora with citation-traceable outputs.}
\resumeItem{Evaluation \& Agentic CI/CD}{Implemented LLM-as-Judge automated evaluation harnesses alongside dual-tracing (Langfuse + OpenTelemetry); deployed containerized agentic services via GitHub Actions CI/CD to GCP Cloud Run, compressing prototype-to-production cycles through automated quality gates.}
\resumeItemListEnd


\resumeSubheading
{Dry Ground AI}{United States of America (Remote)}
{AI Engineer}{Mar. 2025 -- Nov. 2025}
\resumeItemListStart
\resumeItem{AI Voice Agent Development}{Developed and deployed AI voice agents to answer real estate-related calls; integrated tools to retrieve up-to-date information, send messages and emails, and automate client interactions.}
\resumeItem{Client Profiling \& Lead Generation}{Developed a data science workflow for classifying user profiles and identifying potential clients, supporting strategic sales initiatives.}
\resumeItemListEnd


\resumeSubheading
{WEG}{Jaragua do Sul, Brazil}
{Data Scientist}{Jun. 2024 -- Mar. 2025}
\resumeItemListStart
\resumeItem{Predictive Maintenance \& Anomaly Detection}
{Trained an Isolation Forest model to detect anomalies in wind turbine converters, deployed as an API on AWS SageMaker; the model anticipated historical failures by up to two weeks and identified approximately 70\% of the interventions listed in maintenance service orders.}
\resumeItem{Explainability \& Root-Cause Diagnosis}
{Developed a companion SHAP-based API enabling maintenance engineers to diagnose the root causes of detected anomalies, bridging automated detection and corrective action.}
\resumeItem{End-to-End MLOps}
{Built a reproducible MLOps pipeline (MLflow, Docker, Kubernetes, AWS) spanning automated training, versioning, deployment, and live monitoring via Grafana dashboards backed by InfluxDB, enabling iterative model improvements at production scale with full experiment lineage tracking.}
\resumeItemListEnd


\resumeSubheading
{Macnica DHW}{Florianópolis, Brazil}
{Data Scientist}{Nov. 2022 -- Oct. 2023}
\resumeItemListStart
\resumeItem{Smart Sensors}
{Developed an SVM-based classification pipeline for vibration sensor data; applied Multi-objective Genetic Algorithms (NSGA-II via \texttt{pymoo}) to optimize the trade-off between model accuracy and computational efficiency for edge hardware deployment.}
\resumeItem{Computer Vision APIs}
{Built a dual-layer video anonymization API using OpenCV and DBSCAN clustering for motion-based person detection, with a pre-trained ResNet-50-FPN model (PyTorch) as a verification layer; optimized specifically for low frame-rate surveillance footage.}
\resumeItem{IoT Development}
{Led end-to-end IoT product development with full Docker containerization of the edge-to-cloud stack (MQTT Broker, PostgreSQL, InfluxDB, Grafana, Python services); implemented edge computing including FFT calculations directly on Senspider hardware.}
\resumeItemListEnd

\resumeSubheadingAlt
{SSE Gridtech}{Curitiba, Brazil}
{Internship}{Oct. 2014 -- Dec. 2015}
{R\&D Engineer}{Jan. 2016 -- Aug. 2016}
\resumeItemListStart
\resumeItem{Smart Grid \& IoT Solutions}
{Developed a long-range LoRaWAN-based communication system to optimize smart metering infrastructure, reducing GSM dependency.}
\resumeItemListEnd


  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
\resumeSubHeadingListStart

\resumeSubheading
{University of Warwick, Warwick Business School}{Coventry, United Kingdom}
{Research}{Oct. 2019 -- Apr. 2022}
\resumeItemListStart
\resumeItem{Field of Research}
{Ranking \& Selection; Bayesian Optimization; Reinforcement Learning.}
\resumeItem{Research}
{Investigated sample-efficient policy learning for automating constrained supply chain scheduling of biopharmaceutical products (personalized therapies); developed Multi-Objective MCTS (MO-MCTS) using marginal hypervolume as the selection criterion and integrated Evolutionary Algorithms to evolve base policies, combining Bayesian optimization with ranking-and-selection theory.}
\resumeItem{Collaboration}
{Under supervision of Prof. Juergen Branke, we collaborated with Prof. Chun-Hung Chen on two-stage Ranking and Selection (R\&S) problems, which contributed to research extending Optimal Computing Budget Allocation (OCBA) and Expected Value of Information (EVI) algorithms to efficiently allocate finite stochastic simulation budgets on Bayesian approaches for optimal decision-making.}
\resumeItemListEnd

\resumeSubheading
{Shinshu University}{Nagano, Japan}
{MSc Research}{Apr. 2017 -- Mar. 2019}
\resumeItemListStart
\resumeItem{Field of Research}
{Multi-objective Optimization; Genetic algorithms; Evolutionary Computation.}
\resumeItem{Research}
{Studied the impact of Pareto set topologies on multi-objective evolutionary algorithms (MOEAs) and developed a novel method to enhance their performance.}
\resumeItem{International Collaboration}
{Worked with researchers from Japan, Mexico, and France.}
\resumeItem{Recognition}
{Received the Student Best Paper Award at EMO-2019 (Michigan State University, US).}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Shinshu University}{Nagano, Japan}
{Master of Engineering in Electronics and Information System}{Apr. 2017 -- Mar. 2019}
\resumeItemListStart
\resumeItemAlt{}
{MEXT Monbukagakusho Scholarship (Japanese Government)}
\resumeItemListEnd
\resumeSubheading
{Concordia University}{Montreal, Canada}
{Exchange Student, Electrical Engineering}{Aug. 2012 -- Aug. 2013}
\resumeItemListStart
\resumeItemAlt{}
{Science Without Borders Scholarship (Brazilian Government)}
\resumeItemListEnd
\resumeSubheading
{Federal University of Technology - Parana}{Curitiba, Brazil}
{Bachelor of Engineering in Electronics}{Jan. 2010 -- Jul. 2016}
\resumeSubHeadingListEnd

\newpage

%--------TECHNICAL EXPERTISE------------
\section{Technical Expertise}

\begin{tabular}{l @{\quad} p{0.55\linewidth}}
	\textbf{Programming Languages:}& Python, C, C++, Bash (Unix Shell).\\
	\textbf{Frontend Development:}& React, JavaScript, TypeScript, HTML, CSS.\\
	\textbf{AI \& Machine Learning Frameworks:} & PyTorch, Hugging Face Transformers, scikit-learn, XGBoost, LangChain, LangGraph, Google ADK.\\
	\textbf{MLOps \& Deployment Tools:}& Docker, Kubernetes, MLflow, Git, CI/CD, FastAPI, Grafana.\\
	\textbf{Embedded Systems:}& ARM Cortex-M, Jetson Nano, Arduino, FreeRTOS, MQTT.\\
	\textbf{Data Engineering \& Pipelines:}& PostgreSQL, Redshift, InfluxDB.\\
	\textbf{Cloud Platforms:}& AWS (SageMaker, ECR, S3, EC2, Lambda), GCP (Cloud Run, Vertex AI).\\
	\textbf{Optimization:}& Bayesian Optimization, Multi-objective Evolutionary Algorithms.\\
	\textbf{Operating Systems:}& Linux (Fedora, Ubuntu), Windows.\\
\end{tabular}


%-----------PUBLICATIONS-----------------
\section{Publications}
\resumeItemListStart
	\resumeItemAlt{}
	{\textbf{Y. Marca}, H. Aguirre, S. Zapotecas, A. Liefooghe, B. Derbel, S. Verel, and K. Tanaka. Approximating Pareto set topology by cubic interpolation on bi-objective problems. 10th International Conference on Evolutionary Multi-Criterion Optimization (EMO 2019), Lecture Notes in Computer Science (LNCS), Michigan, USA. \textbf{(Best Student Paper Award)}}
	\resumeItemAlt{}
	{\textbf{Y. Marca}, H. Aguirre, S. Zapotecas, A. Liefooghe, B. Derbel, S. Verel, and K. Tanaka. NSGA-II with Spline Interpolation on Bi-objective Problems with Difficult Pareto Set Topology. JPNSEC 2018 Symposium on Evolutionary Computation, Fukuoka, 2018. \textbf{(Young Research Award)}}
	\resumeItemAlt{}
	{\textbf{Y. Marca}, H. Aguirre, S. Zapotecas, A. Liefooghe, B. Derbel, S. Verel, and K. Tanaka. MOEAs on Problems with Difficult Pareto Set Topologies. IEICE Shin-etsu Branch IEEE Session, Niigata University, 2018, p. 169.\textbf{(Young Research Award)}}
	\resumeItemAlt{}
	{\textbf{Y. Marca}, H. Aguirre, S. Zapotecas, A. Liefooghe, B. Derbel, S. Verel, and K. Tanaka. Pareto dominance-based MOEAs on problems with difficult pareto set topologies. In Proceedings of the Genetic and Evolutionary Computation Conference Companion (GECCO '18). ACM, New York, NY, USA, 189-190.}
	\resumeItemAlt{}
	{C. E. A. L. Rocha, \textbf{Y. P. Marca}, F. K. Schneider. Support Platform for Decision-Making in Research and Technological Development in Public Health. ESPACIOS (CARACAS), v. 39, p. 14-26, 2018.}

	\resumeItemAlt{}
	{\textbf{Y. P. Marca}, S. Scholze. Proposta de Substituição da Comunicação GSM em Smart Grids por Rádios de Longo Alcance. XXXIII Simpósio Brasileiro de Telecomunicações, 2015, Juiz de Fora, MG. Anais Completo da Programação Técnica, 2015.}

	\resumeItemAlt{}
	{\textbf{Y. P. Marca}, C. E. A. L. Rocha, B. Schneider Jr , F. K. Schneider. Plataforma de Apoio ao Processo Decisório em Pesquisa e Desenvolvimento Tecnológico em Saúde. Congresso Brasileiro de Engenharia Biomédica, 2012, Porto de Galinhas. ANAIS - CBEB 2012, 2012.}
	\resumeItemAlt{}
	{M. P. Krause, D. M. Nakato, \textbf{Y. P. Marca}, F. K. Schneider. Gerenciamento do Controle da Glicemia Utilizando um Aplicativo para Celular. Congresso Brasileiro de Engenharia Biomédica, 2012, Porto de Galinhas. ANAIS - CBEB 2012, 2012.}

\resumeItemListEnd


%--------LANGUAGES------------
\section{Languages}

\begin{tabular}{l @{\quad} l}
	\textbf{Portuguese:}&Native\\
	\textbf{English:}&Fluent \\
	\textbf{Japanese:}&Conversational \\
\end{tabular}

%-----------PROJECTS-----------------
\section{Projects}


\resumeSubHeadingListStart
\resumeProject
{End-to-End Machine Learning Pipeline for Short-Term Rental Price Prediction}{https://github.com/yurimarca/build-ml-pipeline-for-short-term-rental-prices}
\begin{itemize}
	\item Developed a reproducible ML pipeline to predict short-term rental prices in New York City, ensuring scalability for weekly data updates.
	\item Implemented data ingestion, cleaning, validation, and feature engineering processes to prepare datasets for modeling.
	\item Trained and optimized a Random Forest regression model, employing hyperparameter tuning to enhance predictive performance.
	\item Utilized MLflow for experiment tracking and model management, and integrated Weights \& Biases for artifact tracking and visualization.
	\item Designed the pipeline for seamless retraining with new data, facilitating continuous model improvement and deployment.
\end{itemize}

\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
